\section{Requirements}\label{chap:prjan:sec:req}
In the following section are described the main requirements of this projects.

\begin{longtable}[c]{p{0.3\textwidth}p{0.7\textwidth}}
\hline
\multicolumn{1}{c}{\textbf{Requirement}}                                & \multicolumn{1}{c}{\textbf{Description}}                                                                                                                                                       \\ \hline
\endhead
%
\hline
\endfoot
%
\endlastfoot
%
1. Automatic creation and configuration of NFVI                         & It must be possible to create the environment on which the SFC will be deployed in an automatic manner. The system must support Docker container and exploit Kubernetes as container orchestrator. \\
2. Implementation of chain orchestration and management tools           & The final work must be comprehensive of a minimal software implementation that allows the deployment, the management and the orchestration of VNFs and their lifecycle.                      \\
3. Automatic configuration of chain orchestration and management tools & Software instrumentation for VNFs and SFCs management must be configured automatically, at startup.                                                                                              \\
4. Developing software for manual SFC deployment                        & An instrumentation to deploy a chain of containers in which VNFs can run must be developed. These containers must be able to communicate with each other.                                                \\
5. VNF fault management                                                 & The system must be able to recover a container that has fault automatically.                                                                                                                      \\
6. VNF scalability                                                      & The system must be able to scale the number of containers implementing a function, both augmenting and decrementing their replicas.                                                               \\
7. SFC definition saving                                                & The system must be able to save a definition of a chain                                                                                                                                        \\
8. Deployment/stop/update of a chain from definition                    & The system must be able to allow the deployment of a chain from a saved definition, stop a running SFC and update it.                                                                          \\ \hline
\caption{Table of requirements}
\label{chap:prjan:tab:req}\\
\end{longtable}
